QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-17 Response/Paper_Res.tex
Rev_V6.2

\textcolor{blue}{In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

@@

\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

@@

			\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}

@@

(b) Since DRL methods typically require data in the form of experiences or interaction sequences with an environment, there are no readily available and accessible real datasets that satisfy the core concept of training neural networks (i.e., state, action, reward, and next state) in DRL-based algorithm. We simulated an MEC environment aims to capture the interaction between mobile devices and edge servers, allowing the DRL agent to gain experiences and help generate the necessary data in the desired format for training DRL agents. based on Queuing Theory, Our simulated model provide key system performance metrics, including task delay, energy consumption, and etc, which enable the agent to evaluate each state-action value and define the mobile device's QoE. In this environment, we incorporate multiple mobile devices and edge servers to empower the DRL agents to learn and gather the necessary data for effective training. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. In each time slot, each mobile device generates computation tasks according to a task generation probability. The offloading decision for newly arrived tasks is made by the DRL agent, considering its state that includes the newly arrived task size, the queues information, the MD’s energy level, and the workload history at the ENs. The agents evaluate thair action in that sate by the mobile device's QoE that reflect the key performance metrics based on user preference.

@@

		\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}
		Our main contributions are summarized as follows:
		\begin{itemize}
			\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of mobile devices (MDs), this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs. \vspace{2mm}

>>>>

\textcolor{blue}{In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

@@

\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

@@

			\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}

@@

(b) We appreciate the reviewer’s suggestion regarding the use of a real dataset for evaluation. Since DRL methods typically rely on data in the form of experience or interaction sequences with an environment, there are no readily available real-world datasets that provide the necessary elements for training DRL algorithms (i.e., state, action, reward, and next state). These interactions involve numerous variables and varying application demands, which are rarely captured in publicly available datasets. Capturing real-world interactions between mobile devices and edge servers would require continuous data collection over an extended period to account for the variability in these factors. Besides, ensuring that the dataset covers all possible scenarios, including rare edge cases, is challenging.\vspace{2mm}

\,\,\,\, To capture the interactions between agents and the environment, we carefully simulated an MEC system that allows the DRL agents to gain experience and generate the data required in the proper format for training. As the agent interacts with the environment, it generates new data at each time step, using the system’s feedback (e.g., QoE) to adjust its actions. As mentioned in Section III of the revised manuscript, based on Queuing Theory, our simulated model provides key system performance metrics (for example, task delay, energy consumption, and others), which enable the agent to determine the mobile device's QoE and evaluate each state-action advantage value.\vspace{2mm}

\,\,\,\, For data generation, we adopt a scenario comprising 1,000 episodes. Each episode contains 100 time slots, each of length 0.1 seconds. During each time slot, mobile devices generate computation tasks based on a probabilistic task generation model. The DRL agents make offloading decisions for newly arrived tasks based on their state, which includes information such as task size, queue lengths, the mobile device’s energy level, and the workload history at the edge nodes. The agent evaluates the impact of its actions on the state by assessing the mobile device's QoE, which reflects key performance metrics based on user preferences. The system then transitions to the next state, enabling mobile devices to accumulate the necessary experience through interactions with the MEC environment. As detailed in Section IV-B, these experiences are stored in the replay buffer, creating a rich, continuously growing dataset that represents the diverse conditions and scenarios the agent encounters during computation offloading in MEC.\vspace{2mm}

\,\,\,\, This dynamic, self-generated dataset, by continuous simulation, allows the agent to accumulate a vast and diverse set of training data, representing various interaction sequences between mobile devices and edge servers and ensuring the DRL agent learns optimal strategies for computation offloading.

@@

		\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}
		Our main contributions are summarized as follows:
		\begin{itemize}
			\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of mobile devices (MDs), this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs. \vspace{2mm}

### 2024-10-17 Revision/Paper_Rev.tex
Rev_V6.2

 \textcolor{blue}{In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

>>>>

 %\textcolor{blue}{In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain MEC environments. 
 	%Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. 
 	%Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
  \textcolor{blue}{To capture the dynamic nature of the MEC environment, we leverage the dueling double deep Q-network (D3QN) to strike a balance among QoE factors based on user preferences. Specifically, D3QN improves upon standard DQNs by incorporating both double Q-network and dueling architectures, which reduce overestimation bias in action values and better distinguish the significance of states and actions. Moreover, to effectively handle the uncertainty of the MEC environment where global information is unavailable, we integrate long short-term memory (LSTM) into the D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to proactively adjust their offloading strategies and improve the estimation of long-term QoE.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.
